Using VDMS to Search 100M Images: A Piece of Cake

### 2020-02-17 yfcc100m/paper/vldb2020/design.tex
Add video explanations and other changes
Varios modification to paper files

\section{VDMS Desing and Implementation}
\label{arch}

In this section, we briefly describe VDMS design and implementation,
but most of it is already cover in previous work \cite{vdms-nips}.
Figure \ref{fig:arch} depicts the high-level architecture of VDMS.
VDMS implements a client-server architecture that handles client
requests concurrently and coordinates query execution across
the metadata and data components in order to return a unified response.

The metadata component is the Persistent Memory Graph
Database (PMGD). The (visual) data component is our Visual Compute Module.
The Visual Compute Module enables machine friendly enhancements to
visual data, exposing high-level abstractions to the Request Server for
dealing with a variety of images and video formats (through OpenCV),
and different methods for indexing for Feature Vectors
(including Facebook's Faiss \cite{faiss}, TileDB \cite{TileDB}).
VDMS and its components are fully available open source
\footnote{https://github.com/IntelLabs/\{vdms, pmgd\}}.
We briefly describe each of the main components as follows:

@@

\textbf{Client Library:}
A user application can use the VDMS API by defining metadata conforming to the
query protocol we have defined and passing along blobs. The client side VDMS
library provides a simple query function that accepts a JSON string with
commands and an array or vector of blobs.
Internally, the library wraps the query string and blob using
Google Protobufs \cite{protobufs} and sends it to VDMS.
It also receives a similarly wrapped response from VDMS
and returns it to the client. The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret blobs.
VDMS provides Python and C++ client libraries with mainly
one function: a query that passes metadata as a JSON string and,
optionally, data as a vector of blobs. The VDMS client library manages the
rest.

\textbf{VDMS API:}
VDMS API is easy to use and explicitly predefines certain
visual primitives associated with images, videos, and feature vectors. In
addition, while we use a graph database to store our metadata, the API is not
graph-specific.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based
API\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description},
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between
expressiveness (compared to SPARQL or Gremlim, or even SQL) and
the ability to natively support for visual data operations.
However, it should be possible to achieve similar levels of
expressiveness compared to more mature query languages over time.
The current front-end available are a Python and C++ client
library to provide a simple query function that accepts a JSON string with
commands and an array or vector of blobs.

@@

\begin{itemize}
\item {\em Design for analytics and machine learning}: by targeting
visual data for use cases that require manipulation
of visual information and associated metadata,
\item {\em Ease-of-use}: By defining a common API that allows applications to
combine their complex metadata searches with operations on resulting visual
data, and together with full support for feature vectors, VDMS goes beyond the
traditional SQL or OpenCV level interfaces that do one or the other. Given our
focus on enabling machine learning, we also provide a client API in Python.
\item {\em Performance}: We show how a unified system such as VDMS can
outperform an ad-hoc system constructed with well-known discrete components.
Because of the capabilities we have built into VDMS, it handles complex
queries significantly better than the ad-hoc system without compromising the
performance of simple queries.
\end{itemize}

>>>>

\section{VDMS Design \& Implementation}
\label{arch}

In this section, we briefly describe VDMS design principles and implementation,
(most of it is already cover in previous work \cite{vdms-nips}).
Figure \ref{fig:arch} depicts the high-level architecture of VDMS.
VDMS implements a client-server architecture that handles client
requests concurrently and coordinates query execution across
the metadata and data components in order to return a unified response.

The metadata component is the \textit{Persistent Memory Graph
Database} (PMGD). The (visual) data component is our Visual Compute Module.
The Visual Compute Module enables machine friendly enhancements to
visual data, exposing high-level abstractions to the \textit{Request Server} for
dealing with a variety of images and video formats (through OpenCV),
and different methods for indexing for Feature Vectors
(including Facebook's Faiss \cite{faiss}, TileDB \cite{TileDB}).
VDMS and its components are fully available open source
\footnote{https://github.com/IntelLabs/\{vdms, pmgd\}}.
We briefly describe each of the main components as follows:

@@

\textbf{Client Library:}
A user application can use the VDMS API by defining metadata conforming to the
query protocol we have defined.
The client side VDMS library provides a simple query function that
accepts a JSON string with commands and an array or vector of blobs.
Internally, the library wraps the query string and blob using
Google Protobufs \cite{protobufs} and sends it to the VDMS server.
It also receives a similarly formed response from VDMS
and returns it to the client. The responses require JSON parsing on the client
side for the metadata string that indicates how to interpret blobs field.

\textbf{VDMS API:}
VDMS API is easy to use and explicitly predefines certain
visual primitives associated with metadata, images, videos, and feature vectors.
While we use a graph database to store our metadata,
the API is not graph-specific.
Authors have paid particular attention to hide the complexities of our internal
implementation and up-level the API to a JSON-based
API\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description},
which is very popular across various application domains.
By defining a new JSON-based API, there is a trade-off between
expressiveness (compared to SPARQL or Gremlim, or even SQL) and
the ability to natively support for visual data operations.
However, it should be possible to achieve similar levels of
expressiveness compared to more mature query languages over time.
The current front-end available are a Python and C++ client
library to provide a simple query function that accepts a JSON string with
commands and an array or vector of blobs.

@@

\begin{itemize}
\item {\em Design for analytics and machine learning}: by targeting
visual data for use cases that require manipulation
of visual information and associated metadata,
\item {\em Ease-of-use}: By defining a common API that allows applications to
combine their complex metadata searches with operations on resulting visual
data, and together with full support for feature vectors, VDMS goes beyond the
traditional SQL or OpenCV level interfaces that do one or the other.
\item {\em Performance}: We show how a unified system such as VDMS can
outperform an ad-hoc system constructed with well-known discrete components.
Because of the capabilities we have built into VDMS, it handles complex
queries significantly better than the ad-hoc system without compromising the
performance of simple queries.
\end{itemize}
